White Dwarf Mergers on Adaptive Meshes\\ II. Collisions

### 2017-07-11 papers/wdmerger_II/paper.tex
Add comments on suppressed burn variants

In contrast, the suppressed burning mode (modeled after \citet{kushnir:2013}) produces only about
$5 \times 10^{-4}\ \msolar$ of $^{56}$Ni. In a suppressed burn, we ensure that at every evaluation
of the right-hand-side vector for the nuclear network integration, all quantities are scaled by the
same factor, with this factor ensuring that the energy release is not large enough to permit a
spurious detonation. This seems to be equivalent to the method used in \citet{kushnir:2013}. We
reproduce their claim that this suppresses the detonation until later in the collision, after more
material has approached the stalled shock. We also observe that, for a given resolution, the simultaneous
detonations occur slightly outside the initial contact point, near the edges of the stalled shock. They
establish as the main source of error in simulations that produce too little nickel. However, we find
that the resulting detonations are not strong enough to convert a significant amount of material to NSE
conditions; instead, only QSE conditions are reached near the center of the collision, leaving a significant
amount of silicon and sulfur on the domain that is not further processed.

>>>>

In contrast, the suppressed burning mode (modeled after \citet{kushnir:2013}) produces only about
$5 \times 10^{-4}\ \msolar$ of $^{56}$Ni. In a suppressed burn, we ensure that at every evaluation
of the right-hand-side vector for the nuclear network integration, all quantities are scaled by the
same factor, with this factor ensuring that the energy release is not large enough to permit a
spurious detonation. This seems to be equivalent to the method used in \citet{kushnir:2013}. We
reproduce their claim that this suppresses the detonation until later in the collision, after more
material has approached the stalled shock. We also observe that, for a given resolution, the simultaneous
detonations occur slightly outside the initial contact point, near the edges of the stalled shock. They
establish as the main source of error in simulations that produce too little nickel. However, we find
that the resulting detonations are not strong enough to convert a significant amount of material to NSE
conditions; instead, only QSE conditions are reached near the center of the collision, leaving a significant
amount of silicon and sulfur on the domain that is not further processed. In order to ensure that the
very different results we obtained were not a result of the specific choice we made for how to suppress
the burn, we tried varying the approach discussed in \autoref{sec:burner}. First, we limited based on
the current value of the internal energy and sound speed rather than the fixed, initial value during a burn
(this should be a less severe limiter). This did not yield a significant difference in the outcome. Second,
we also tried applying the limiting after the burn had completed, using the differences between the input
and output states of the integration, rather than directly limiting the RHS in the ODE. The behavior of the
burn was qualitatively different, in that nickel production began much earlier in the collision when the limiting
was applied this way. Nevertheless, the qualitative final outcome of the collision -- only trace amounts
of nickel produced in total -- was still unchanged. With this variant too, it did not matter whether the limiting
factor was determined based on the initial value of the state or the final value of the state.
